NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-09-12 ms_nihao_budget.tex
new plot for comparason by including Christensen+16

%% FIGURE 2
\begin{figure}
\centerline{
  \psfig{figure=m500c_frac.eps,width=0.48\textwidth}
}
\caption{{\bf Baryon fraction within R$_{500}$ comparing with \citet{Voort16}.
   The blue points are from NIHAO simulations and the red pentagons are from
   FIRE simulations.}}
\label{fig:fire_com}
\end{figure}

@@

{\bf \citet{Christensen16} run twenty galaxy simulations spanning the mass range
from $10^{9.5} - 10^{12} \Msun$ using zoom-in cosmological hydrodynamic 
simulation code and didn't only reproduce the stellar mass - halo mass
relation but also showed a similar baryon fraction relation, e.g. in 
L$^*$ galaxies, the fraction is reduced by 20\% while in galaxies with
halo mass $< 10^{10} \Msun$ there can be as large as an 80\% mass reduction.
This suggests that the potential well of the halo regulates the baryon
fraction.
To compare with baryon fraction in \citet{Voort16}, we derive
the M$_{500}$ and R$_{500}$ to recalculate the ratio between 
baryon fraction to the universal fraction of baryons. The baryon
fraction have good agreement with each other in the whole mass range
where NIHAO simulations explored. For the massive haloes with 
M$_{500} > 10^{12} \Msun$, there are two galaxies from NIHAO have
reduced baryon fraction and four more massive galaxies from FIRE
have larger reduced baryon fraction which may hint that the baryon
fraction will decrease as the halo mass increases in large mass range.}

>>>>

%% FIGURE 2
\begin{figure*}
\centerline{
  \psfig{figure=m500c_frac.eps,width=1.00\textwidth}
}
\caption{{\bf Upper panel shows baryon fraction comparing with 
   \citet{Voort16} (left) and \citet{Christensen16} (right), and lower
   panel shows stellar fraction comparing with \citet{Voort16} (left) 
   and \citet{Christensen16} (right).
   The blue points are from this work, the red pentagons are from
   \citet{Voort16} and the magenta pentagons are from 
   \citet{Christensen16}.}}
\label{fig:fire_com}
\end{figure*}

@@

{\bf \citet{Christensen16} run twenty galaxy simulations spanning the mass range
from $10^{9.5} - 10^{12} \Msun$ using zoom-in cosmological hydrodynamic 
simulation code and didn't only reproduce the stellar mass - halo mass
relation but also showed a similar baryon fraction relation, e.g. in 
L$^*$ galaxies, the fraction is reduced by 20\% while in galaxies with
halo mass $< 10^{10} \Msun$ there can be as large as an 80\% mass reduction.
This suggests that the potential well of the halo regulates the baryon
fraction.
Meanwhile, \citet{Voort16} have similar result produced by zoom-in 
cosmological hydrodynamic simulation suit FIRE which has 16 galaxies 
with similar halo mass range.
Fig.~\ref{fig:fire_com} compares baryon and stellar fraction with 
\citet{Voort16} and \citet{Christensen}, we derive
new baryonic mass and stellar mass within R$_{500}$ and R$_{100}$
to make sure the ratios compared in each panel have same definitions with
ratios from other simulation suites. The baryon fraction in NIHAO simulations
have good agreement with both of the simulation suite in the whole mass range
where NIHAO simulations explored. For the massive haloes with 
M$_{500} > 10^{12} \Msun$, there are two galaxies from NIHAO have
reduced baryon fraction and four more massive galaxies from FIRE
have larger reduced baryon fraction which may hint that the baryon
fraction will decrease as the halo mass increases in large mass range.
For stellar fraction, \citet{Voort16} shows a almost same result with
our work, even at low mass range, the two galaixes may suggest the 
large scatter as we produced.}
